---
title: 'STA437: Project presentation'
author: "Joël Meili"
date: "6/7/2022"
output: 
  beamer_presentation:
    theme: "Boadilla"
    colortheme: "whale"
    fonttheme: "structurebold"
    slide_level: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

require(png)
require(grid)
require(gridExtra)
```

## Agenda
- Data set
- Comparison between Adam and SGD optimizer
- Code availability

## Data set
- The data set consists out of 199 chest CT volumes of patients with positive RT-PCR for SARS-CoV2
- The goal of the data set is to annotate lesions in the lung CT
- The data can be found here: [**https://covid-segmentation.grand-challenge.org/**](https://covid-segmentation.grand-challenge.org/)

## Comparison between Adam and SGD optimizer
- Adam performs better than SGD for all three learning rates: 1e-3, 1e-4 and 1e-5

```{r}
g1 <- rasterGrob(as.raster(readPNG("figures/optimizer_comparison_0_train_loss.png")), interpolate = FALSE)
g2 <- rasterGrob(as.raster(readPNG("figures/optimizer_comparison_1_train_loss.png")), interpolate = FALSE)
g3 <- rasterGrob(as.raster(readPNG("figures/optimizer_comparison_2_train_loss.png")), interpolate = FALSE)

g4 <- rasterGrob(as.raster(readPNG("figures/optimizer_comparison_0_val_loss.png")), interpolate = FALSE)
g5 <- rasterGrob(as.raster(readPNG("figures/optimizer_comparison_1_val_loss.png")), interpolate = FALSE)
g6 <- rasterGrob(as.raster(readPNG("figures/optimizer_comparison_2_val_loss.png")), interpolate = FALSE)

grid.arrange(g1, g2, g3, g4, g5, g6, ncol = 3, nrow = 2)
```

## Model inference

## Code availability
- The source code is available in this Github repository: [**https://github.com/joelmeili/STA437/**](https://github.com/joelmeili/STA437/)
